Synthesizing Symmetric Lenses

### 2018-07-12 papers/SymmetricLenses/main.tex
fits in 25 pages

\begin{figure}
  \setlength\extrarowheight{3pt}
  \begin{tabular}{@{\hspace*{5em}}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)\Probability_2}{1 - \Probability_1\Probability_2}})}{\Probability_1\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
  \caption{Stochastic Regular Expression Star-Semiring Equivalence}
  \label{fig:ssr-sre}
\end{figure}

@@

All three sources for our benchmarks provide realistic problems suitable for
answering the research questions: Flash Fill data cleaning tasks are either
derived from online help forums or taken from the Excel product team; Augeas is
a utility that transforms Linux configuration files into a manageable dictionary
form; and many of the remaining benchmarks arise from synchronizing real-world
data formats such as BibTeX and EndNote.  Each task consists of a source and
target regular expression.\saz{Do we want to say anything about the sizes of these?}

@@

To determine whether the system can synthesize the desired lenses, we ran the
symmetric synthesis algorithm interactively on all 48 tasks,
working with the system to create sufficient examples and adjust the termination
parameter.  In all cases, the desired lens was obtained, which we verified by
manually inspecting the generated lens programs.
%
The majority of the tasks required only a single example and none required
more than three examples in order to synthesize the desired lens.\footnote{In
  one benchmark, we supplied a fourth example that was later discovered to 
  be unnecessary.}

>>>>

\begin{figure}
  \begin{tabular}{@{\hspace*{5em}}r@{\hspace{1em}}c@{\hspace{1em}}l@{}r@{}}
    \PRegexOr{\Regex}{\emptyset}{1} & $\SSREquiv$ & \Regex{} & \OrIdentityRule{} \\
    $\RegexConcat{\Regex}{\emptyset}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionRightRule{} \\
    $\RegexConcat{\emptyset}{\Regex}$ & $\SSREquiv$ & $\emptyset$ & \EmptyProjectionLeftRule{} \\
    \RegexConcat{(\RegexConcat{\Regex{}}{\Regex'})}{\Regex''} & $\SSREquiv$ & \RegexConcat{\Regex{}}{(\RegexConcat{\Regex'}{\Regex''})} & \ConcatAssocRule{}  \\
    \PRegexOr{(\PRegexOr{\Regex}{\Regex'}{\Probability_1})}{\Regex''}{\Probability_2} & $\SSREquiv$ & \PRegexOr{\Regex}{(\PRegexOr{\Regex'}{\Regex''}{\frac{(1-\Probability_1)\Probability_2}{1 - \Probability_1\Probability_2}})}{\Probability_1\Probability_2} & \OrAssociativityRule{}  \\
    \PRegexOr{\Regex{}}{\RegexAlt{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\RegexAlt{}}{\Regex{}}{1-\Probability} & \OrCommutativityRule{}\\
    \RegexConcat{\Regex{}}{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}}{\Regex{}'})}{(\RegexConcat{\Regex{}}{\Regex{}''})}{\Probability} & \DistributivityLeftRule{} \\
    \RegexConcat{(\PRegexOr{\Regex{}'}{\Regex{}''}{\Probability})}{\Regex{}} & $\SSREquiv$ & \PRegexOr{(\RegexConcat{\Regex{}'}{\Regex{}})}{(\RegexConcat{\Regex{}''}{\Regex{}})}{\Probability} & \DistributivityRightRule{} \\
    \RegexConcat{\EmptyString{}}{\Regex{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityLeftRule{} \\
    \RegexConcat{\Regex{}}{\EmptyString{}} & $\SSREquiv$ & \Regex{} & \ConcatIdentityRightRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\Regex{}}{\PRegexStar{\Regex{}}{\Probability}})}{1-\Probability} & \UnrollstarLeftRule{} \\
    \PRegexStar{\Regex{}}{\Probability} & $\SSREquiv$ & \PRegexOr{\EmptyString{}}{(\RegexConcat{\PRegexStar{{\Regex{}}}{\Probability}}{\Regex{}})}{1-\Probability} & \UnrollstarRightRule{} 
  \end{tabular}
  \caption{Stochastic Regular Expression Star-Semiring Equivalence}
  \label{fig:ssr-sre}
\end{figure}

@@

All three sources provide realistic problems suitable for
answering the research questions: Flash Fill data cleaning tasks are either
derived from online help forums or taken from the Excel product team; Augeas is
a utility that transforms Linux configuration files into a manageable dictionary
form; and many of the remaining benchmarks arise from synchronizing real-world
data formats such as BibTeX and EndNote.  Each task consists of a source and
target regular expression.\saz{Do we want to say anything about the sizes of these?}

@@

To determine whether the system can synthesize the desired lenses, we ran it
interactively on all 48 tasks, working with the system to create sufficient
examples and adjust the termination parameter.  In all cases, the desired lens
was obtained, which we verified by manually inspecting the generated lens
programs.
%
The majority of the tasks required only a single example and none required
more than three examples in order to synthesize the desired lens.\footnote{In
  one benchmark, we supplied a fourth example that was later discovered to 
  be unnecessary.}
